\simname 2.0 User's Guide

### 2009-08-14 doc/manual.tex
update booksim manual
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/trunk@1427 ce7aba0d-9f81-40a6-a495-cecae84b0515

\author{Ted Jiang, George Michelogiannakis, Daniel Becker, Brian Towles and William J. Dally}
\title{\simname 2.0 User's Guide}

@@

\subsubsection[Batch mode]
Batch mode is enabled by setting \texttt{use\_read\_write= 1}. In batch mode, \texttt[injection\_rate] paramter is ignored. Instead, traffic are injected into the network as fast as possible until \texttt{batch\_size} of request packets are generated by each node. When a destination node receives a request packet, it returns a reply packet. The total number of packets injected in batch mode is 2$\times$ \texttt{batch\_size} per node. The parameter \texttt[max\_outstanding] specifies the maximum number of (request or reply) packets waiting at a node to be injected into the network.

\subsubsection[Traffic Patterns]
The simulator also supports several different traffic patterns that
are specified using the \texttt{traffic} option.  To describe these
patterns, we use the same notation of PPIN Section 3.2: $s_i$ ($d_i$)
denotes the $i^\textrm{th}$ bit of the source (destination) address
whereas $s_x$ ($d_x$) denotes the $x^\textrm{th}$ radix-$k$ digit of
the source (destination) address.  The bit length of an address is $b
= \log_2 N$, where $N$ is the number of nodes in the network.

>>>>

\author{Nan Jiang, George Michelogiannakis, Daniel Becker, Brian Towles and William J. Dally}
\title{\simname 2.0 User's Guide}

@@

\subsubsection{Batch mode}
Batch mode is enabled by setting \texttt{use\_read\_write= 1}. In batch mode, \texttt[injection\_rate] paramter is ignored. Instead, traffic are injected into the network as fast as possible until \texttt{batch\_size} of request packets are generated by each node. When a destination node receives a request packet, it returns a reply packet. The total number of packets injected in batch mode is 2$\times$ \texttt{batch\_size} per node. The parameter \texttt[max\_outstanding] specifies the maximum number of (request or reply) packets waiting at a node to be injected into the network.

\subsubsection{Traffic Patterns}
The simulator also supports several different traffic patterns that
are specified using the \texttt{traffic} option.  To describe these
patterns, we use the same notation of PPIN Section 3.2: $s_i$ ($d_i$)
denotes the $i^\textrm{th}$ bit of the source (destination) address
whereas $s_x$ ($d_x$) denotes the $x^\textrm{th}$ radix-$k$ digit of
the source (destination) address.  The bit length of an address is $b
= \log_2 N$, where $N$ is the number of nodes in the network.
